A comparison of classification algorithms applied to the Adult Database

### 2009-12-10 report/final.tex
added id3 results.

\begin{table}
  \begin{center}
  \begin{tabular}{ | l | c | c | c | c | c |}
    \hline
    \textbf{Type} & \textbf{Criterion} & \textbf{Train error rate} & \textbf{Test error rate} & \textbf{Time} \\ \hline
    ID3 & Gain Ratio & 0 & 0 & 0 \\ \hline
    ID3 & Information Gain & 0 & 0 & 0 \\ \hline
    ID3 & Gini Index & 0 & 0 & 0 \\ \hline
    ID3 & Accuracy & 0 & 0 & 0 \\ \hline
    ID3 Numerical & Gain Ratio & 0 & 0 & 0 \\ \hline
    ID3 Numerical & Information Gain & 0 & 0 & 0 \\ \hline
    ID3 Numerical & Gini Index & 0 & 0 & 0 \\ \hline
    ID3 Numerical & Accuracy & 0 & 0 & 0 \\ \hline
  \end{tabular}
  \caption{Results for ID3.}
  \label{tbl:results_id3}
  \end{center}
\end{table}

>>>>

\begin{table}
  \begin{center}
  \begin{tabular}{ | l | c | c | c | c | c |}
    \hline
    \textbf{Type} & \textbf{Criterion} & \textbf{Train error rate} & \textbf{Test error rate} & \textbf{Time} \\ \hline
    ID3 & Gain Ratio & 18.38 & 18.61 & 0m04s \\ \hline
    ID3 & Information Gain & 18.48 & 19.05 & 0m03s \\ \hline
    ID3 & Gini Index & 18.94 & 19.15 & 0m04s \\ \hline
    ID3 & Accuracy & 20.41 & 20.24 & 0m04s \\ \hline
    ID3 Numerical & Gain Ratio & 14.93 & 15.68 & 0m14s \\ \hline
    ID3 Numerical & Information Gain & 15.68 & 16.42 & 0m06s \\ \hline
    ID3 Numerical & Gini Index & 16.10 & 16.96 & 0m07s \\ \hline
    ID3 Numerical & Accuracy & 17.99 & 17.92 & 0m12s \\ \hline
  \end{tabular}
  \caption{Results for ID3.}
  \label{tbl:results_id3}
  \end{center}
\end{table}
